### 2021-06-01 paper/NIHGrant.tex
minor edits

To reconstruct cognitive representations of tinnitus from a binary classification task.
Participants will classify white noise stimuli as sounding like their tinnitus or not.
Reverse correlation will be used to infer an unbiased estimate of each participant's
cognitive representation of their tinnitus percept.

@@

To enhance the efficiency of reverse correlation using compressive sensing,
which requires significantly fewer samples to achieve convergent accuracy.
The reverse correlation and compressive sensing framework will be released
as an open-source software implementation for use by the research community.
Our pilot data demonstrates that compressive sensing affords a 90\% decrease
in the number of trials for equivalent resultant latent representation.

@@

To characterize cognitive representations of tinnitus between participants and over time.
Dimensionality reduction algorithms will reveal latent similarities between
tinnitus representations which will be subtyped using a data-driven approach.

@@

Current methods to determine cognitive representations of tinnitus
are inefficient and introduce bias, resulting in a lack of standardization in tinnitus assessment \cite{henryTinnitusEpidemiologicPerspective2020}.
One common method is the alternate forced-choice (AFC) paradigm task, which asks the patient to determine which of two sounds
is closer to their tinnitus percept
\cite{henryComparisonTwoComputerautomated2001,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013,korthOneStepCloser2020}.
Recent computer and methodological advances have made the test more portable and efficient,
but the AFC paradigm still relies on assumptions about the subject's tinnitus percept.
Tinnitus percepts are too heterogeneous to be represented by pure tones or small-envelope waveforms.
\autoref{fig:tinnitusexamples} displays spectrograms of example tinnitus percepts
from the American Tinnitus Association website,
showing the heterogeneity of tinnius percepts as well as their richness in frequency spectra and temporal characteristics.
Adequately sampling the psychoacoustic space of possible tinnitus percepts via an AFC task is unfeasible.
Other approaches have attempted to capture the richness of tinnitus percepts using likeness measures,
in which the subject rates whether a presented stimulus is part of their tinnitus percept or not \cite{norenaPsychoacousticCharacterizationTinnitus2002}.
While this method is able to capture more features of cognitive representations of tinnitus,
it is time-consuming and limited by the aural skills of the subject \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
Both these approaches involve the subject comparing an external stimulus to their cognitive representation of the tinnitus percept,
however AFC tasks introduce biases by artificially limiting the stimulus space and likeness measures are time-consuming.
\emph{We believe that a novel reverse correlation-based approach will produce efficient and unbiased cognitive representations of tinnitus percepts}
\cite{gosselinSuperstitiousPerceptionsReveal2003}.

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_6.png}
	\caption{Examples of tinnitus spectrograms from the American Tinnitus Association website.
	These spectrograms are heterogeneous as well as high-dimensional; the signals contain many frequency bands and vary over time.}
	\label{fig:tinnitusexamples}
\end{figure}

@@

Reverse correlation, in addition to its prominence as an important tool relative to lower-level
neural mechanisms, has been increasingly used for inferring higher-level cognitive representations,
including psychophysical kernels that drive the top-down processes of perception
\cite{ahumadaStimulusFeaturesSignal1971, neriReceptivePerceptiveFields2006,gosselinSuperstitiousPerceptionsReveal2003,smithMeasuringInternalRepresentations2012}, 
and even abstract psychological
categories (\eg ``male'' vs. ``female'' faces; \cite{brinkmanVisualisingMentalRepresentations2017,manginiMakingIneffableExplicit2004,ponsotCrackingSocialCode2018}.
Recent work in vision has demonstrated that
reverse correlation can effectively characterize cognitive representations underlying letter and face
recognition \cite{gosselinSuperstitiousPerceptionsReveal2003,liuSeeingJesusToast2014}.
One speech study has also estimated steady-state representations of vowels the /a/
and /i/ using a closely-related paradigm to the one proposed here (Fig 2B; \cite{brimijoinInternalRepresentationVowel2013}). Our
proposed use of reverse correlation in the domain of speech expands on classic efforts to understand
top-down processing in speech with the presentation of rich, vague stimuli to elicit responses from
listeners \cite{warrenAuditoryIllusionsConfusions1970,vokeySubliminalMessagesDevil1985}.
These studies provide clear evidence that rich
stimuli, such as white noise, are sufficient to engage the top-down process, even if they do not attempt to
characterize the latent representations.

Incomplete characterizations of cognitive representations impoverish our scientific understanding of tinnitus,
weak causal explanations for its etiology, and hinder progress towards effective treatments.
Reverse correlation shows promise to provide a more complete characterization of cognitive representations of tinnitus
and is applicable to other psychophysical domains as well.
Directly characterizing complex representations of tinnitus can enable more effective, targeted treatments,
reveal insights about subtypes of the condition, and pave the way for new tinnitus-masking assistive devices.
Fully characterizing a high-dimensional representation of tinnitus will improve causal explanations
for currently unexplained variability in tinnitus experience both between subjects and within single subjects over time.

\begin{description}
	\item[A.3. Rigor of the Prior Research]{}
\end{description}

@@

In the proposed project, we will use reverse correlation to reveal unbiased high-dimensional
representations of tinnitus and further characterize the condition
using dimensionality-reduction and density-based clustering.
In \emph{Aim \#1}, we will develop and run an experimental paradigm
in which tinnitus patients listen to noisy stimuli and perform an alternate forced-choice task
answering the question, ``Does this sound like your tinnitus?''
Reverse correlation frees us from the methodological constraint of imposing strong \emph{a priori}
assumptions about the tinnitus percept.
In \emph{Aim \#2}, we will develop an open-source signal processing pipeline
to reconstruct cognitive representations of tinnitus using compressive sensing.
Compressive sensing holds promise to dramatically reduce the number of samples
needed for accurate reconstruction, enabling us to run more experimental subjects for Aim \#1,
and retest subjects to examine the stability of cognitive representations of tinnitus over time.
\emph{Aim \#3} contextualizes reconstructed cognitive representations of tinnitus
by visualizing underlying subtypes or clusters on a lower dimensional manifold.
We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
providing direct insight into commonalities and variability of tinnitus experience in and between subjects.

@@

One approach is to use forced-choice selection tasks.
In this experimental paradigm,
the experimenter presents participants with multiple samples of auditory stimuli that vary in well-characterized
and often highly-constrained ways, along specific dimensions (\eg pure tone frequency, width of spectral envelope)
that are known to be, or are hypothesized to be, relevant to tinnitus representation or masking
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryMeasurementTinnitus2016}.
The subject then makes a choice between stimuli.
While new methodological advances in experiment design and technology have streamlined this approach
\cite{korthOneStepCloser2020,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013},
it is still constrained by \emph{a priori} assumptions about the nature of tinnitus percepts.
In contrast, likeness approaches use subjective judgment tasks,
in which the subject rates how much (if at all) a presented stimulus is part of or masks their tinnitus percept
\cite{norenaPsychoacousticCharacterizationTinnitus2002}.
While likeness measures provide more complete reconstructions of tinnitus cognitive representations,
likeness tests are time-consuming and generally not used in clinical practice
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.

@@

Reverse correlation has been applied across multiple fields to reveal underlying representations by application of unconstrained, noisy input.
It has been used to characterize low-level latent representations encapsulated in neural tuning
(\eg receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004}
and has been used to successfully recover cognitive representations underlying visual perception \cite{gosselinSuperstitiousPerceptionsReveal2003,}
Both existing experimental work (\cf Fig 2B in \cite{brimijoinInternalRepresentationVowel2013})
and our preliminary simulation experiments (\autoref{fig:csexample}) suggest that this method can be successfully translated
into the auditory domain.
Reverse correlation allows us (1) to uncover more complex, potentially higher-dimensional representations
than would be possible using more focused, constrained stimuli,
(2) to recover directly the nature of the representations themselves rather than the relation
between the tinnitus percept and a masking sound,
and (3) to recover cognitive representations of the tinnitus percept directly rather than a neural correlate.
In short, reverse correlation will be able to provide deeper understanding of cognitive representations of tinnitus percepts
than is possible with conventional methods.

@@

Our preliminary testing suggests that truly random envelopes
often result in the perception of colored noise.
Minimal additional spectral-temporal constraints may need to be imposed on stimuli
such that participants will interpret the stimuli as intending to be tinnitus percepts.
This is similar to the approach taken in some visual domain experiments,
where bandlimited random stimuli, or stimuli with partial superimposed templates,
are presented \cite{smithMeasuringInternalRepresentations2012} (\hl{CITE}).
The basic approach will be to use inverse Fourier transforms to generate 0.5-s noise stimuli
including frequencies from 0.1 to 22 kHz.
We will impose minimal constraints on the stimuli generation process,
in order to selectively generate stimuli approaching the heterogeneous samples of tinnitus percepts
provided by the American Tinnitus Association on their website.

@@

During the experiment, subjects will be asked to perform an computerized alternate forced-choice task,
selecting whether the presented stimulus sounds similar to their tinnitus percept or not.
Each signal will be presented to subjects over headphones
at a comfortable listening level ($\approx 75$ dB SPL).
Subjects will be asked to perform the task in hour-long blocks with a rest period in-between.
Subjects can perform the task for one or more blocks at their choice,
and will be compensated for their participation.

@@

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_3.png}
	\caption{Schematic overview of experiments proposed in Aim \#1.
	Subjects are presented with random stimuli,
	which is compared to a latent internal representation.
	Reverse correlation is used to reconstruct the latent internal representation
	from many trials.
	Simulation results are shown, demonstrating proof-of-concept
	for the proposed reverse correlation paradigm.}
	\label{fig:experiment}
\end{figure}

@@

We have conducted simulation studies to begin validating compressive sensing
for improving the efficiency of reverse correlation.
Fpr example, using a template time-frequency representation, $x$,
as a proxy for the latent representation of interest,
we generate plausible yes/no subject responses, $y \in \{-1, 1\})$,
based on the similarity between the template
and a random stimuli (\ie $y = \mathrm{sign}(\phi x)$ for stimuli $\phi$).
Estimation of the template is performed using
(\emph{a}) convention regression-based reverse correlation
(\ie $\hat{x}_c = n^{-1} X^\mathrm{T}y$) \cite{gosselinSuperstitiousPerceptionsReveal2003},
or (\emph{b}) compressive sensing.

@@

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=\textwidth]{Figures/CompSensExamples.pdf}
	\caption{Compressive sensing (CS) delivers accurate signal reconstruction from sampling
	with a comparatively small number of samples.
	The latent representation in (\emph{A}) is estimated in (\emph{B-E}).
	In (\emph{B-C}) conventional regression-based estimation is used
	and in (\emph{D-E}) compressive sensing is used.
	The number of samples $n$ is displayed along with the correlation coefficient $r^2$
	between the estimated reconstruction and the original signal,
	as a measure of reconstruction quality.}
	\label{fig:csexample}
\end{figure}

@@

Surveys of tinnitus patients have identified sixteen qualitative subtypes of tinnitus
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,meikleTinnitusArchiveArchive2004,stoufferCharacterizationTinnitusTinnitus1990},
but these categories are limited by the fuzziness of linguistic categories and the musical ability of the tinnitus patients.
One tinnitus patient we interviewed, who has a degree in music performance,
was able to identify her tinnitus as sounding like a particular note played on the crotales,
a niche percussion instrument.
For most tinnitus patients who lack the depth of vocabulary to explain their tinnitus percept that precisely,
linguistic description of tinnitus can be vague and overlapping.
For instance, two of the aforementioned categories are ``high tension wire'' and ``transformer noise,''
which may mean different things to different people and are difficult to disambiguate.
Therefore, we propose to perform a quantitative analysis of the recovered high-dimensional tinnitus percepts
to reveal data-driven latent subtypes of tinnitus.

We will perform a quantitative analysis based on latent variable analysis methods.
Latent variable methods relate observed variation (\eg in tinnitus representations)
to latent variables that capture the observed variation (\eg major variation types across tinnitus percepts).
We will use principle component analysis (PCA), t-stochastic neighbor embedding (t-SNE; \cite{vandermaatenBarnesHutSNE2013}),
and uniform manifold approximation and projection (UMAP; \cite{mcinnesUMAPUniformManifold2020}).
Applying these dimensionality-reduction algorithms to a collection of representations
will identify major modes of variation across those representations,
uncovering latent similarities between representations.
Clusters of data points become readily visible in the lower-dimensional manifold generated
by these unsupervised machine learning methods, each of which represents
a data-driven tinnitus subtype (\autoref{fig:dimredexample}).
We will characterize these subtypes, identifying their properties and assigning them descriptive names.
In the case of PCA and UMAP, new data can be mapped into the lower-dimensional manifold,
allowing representations from new subjects to be classified into these subtypes.

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/umap.png}
	\caption{Tinnitus representations with different spectral characteristics cluster in a lower dimensional manifold.
	Tinnitus representation waveforms were generated using examples from the American Tinnitus Association website with added Gaussian noise.
	(\emph{a}) shows the frequency spectra for representative waveforms. In (\emph{b}), the waveforms
	are dimensonally-reduced using UMAP from 8,193 dimensions to 2.
	The waveforms cluster in this lower dimensional, revealing latent similarities.}
	\label{fig:dimredexample}
\end{figure}

@@

In Aim \#1, we generate stimuli by randomly sampling Fourier coefficients from a flat distribution to generate a spectrum.
We enforce minimal constraints on the stimuli (\eg that the frequency content is audible).
This has the benefit of reducing bias in the reconstructed representations,
but results in experiments that take longer to converge to a good reconstruction.
Previous studies using reverse correlation have attempted to reduce noise in the reconstructed representation
(and thus converge much faster) by carefully selecting stimuli biased towards a certain representation.
For example, Smith and colleagues \cite{smithMeasuringInternalRepresentations2012}
devised a task to uncover cognitive representations of faces using reverse correlation,
using pictures of human faces distorted by noise as stimuli for the task.
While this allowed the experimenters to perform fewer trials to achieve good reconstructions,
it introduced bias of what experimenters think human faces look like (by selecting the pictures),
defeating one of the main advantages of reverse correlation.

>>>>

To reconstruct perceptual representations of tinnitus using a novel reverse correlation procedure. Participants with tinnitus will be presented with richly varying stimuli in the context of a yes-no behavioral response paradigm. Perceptual representations can be estimated by regressing observed responses against the stimuli over many trials. Reconstructed representations will be compared to conventional estimates of tinnitus from the same participants. Expected outcome: reconstructed representations of tinnitus will more detailed and less biased than any those obtained through conventional methods.

@@

To enhance the efficiency of the reverse correlation procedure using compressive sensing, which substantially reduces the number of trials required to accurately reconstruct perceptual representations. We will use compressive sensing to more efficiently and more accurately reconstruct cognitive representations using data obtained in Aim \#1. Expected outcome: compressive sensing is expected to improve efficiency of the reverse correlation procedure by up to 90\%.
% The reverse correlation and compressive sensing framework will be released
% as an open-source software implementation for use by the research community.
% Our pilot data demonstrates that compressive sensing affords a 90\% decrease
% in the number of trials for equivalent resultant latent representation.

@@

To characterize variability in perceptual representations of tinnitus between participants and over time. We will use unsupervised machine learning techniques to reveal latent similarities between tinnitus representations, and subsequently cluster those into distinct categories. Expected outcome: Unsupervised machine learning will identify distinct categories of tinnitus, which will allow us to further improve the effiency and accuracy of uncovering tinnitus representations through improved stimulus generation and representation classification.

% Dimensionality reduction algorithms will reveal latent similarities between
% tinnitus representations which will be subtyped using a data-driven approach.

@@

Current methods to determine cognitive representations of tinnitus
are inefficient and introduce bias, resulting in a lack of standardization in tinnitus assessment \cite{henryTinnitusEpidemiologicPerspective2020}.
One common method is the alternate forced-choice (AFC) paradigm task, which asks the patient to determine which of two sounds
is closer to their tinnitus percept
\cite{henryComparisonTwoComputerautomated2001,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013,korthOneStepCloser2020}.
Recent computer and methodological advances have made the test more portable and efficient,
but the AFC paradigm still relies on assumptions about the subject's tinnitus percept.
Tinnitus percepts are too heterogeneous to be represented by pure tones or small-envelope waveforms.
\autoref{fig:tinnitusexamples} displays spectrograms of example tinnitus percepts
from the American Tinnitus Association website,
showing the heterogeneity of tinnius percepts as well as their richness in frequency spectra and temporal characteristics.
Adequately sampling the psychoacoustic space of possible tinnitus percepts via an AFC task is unfeasible.
Other approaches have attempted to capture the richness of tinnitus percepts using likeness measures,
in which the subject rates whether a presented stimulus is part of their tinnitus percept or not \cite{norenaPsychoacousticCharacterizationTinnitus2002}.
While these methods capture more features of cognitive representations of tinnitus,
they are time-consuming and limited by the aural skills of the subject \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.
Both AFC and likeness measures involve the subject comparing an external stimulus to their cognitive representation of the tinnitus percept,
however AFC tasks introduce biases by artificially limiting the stimulus space and likeness measures are time-consuming.
\emph{We believe that a novel reverse correlation-based approach will produce efficient and unbiased cognitive representations of tinnitus percepts}
\cite{gosselinSuperstitiousPerceptionsReveal2003}.

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_6.png}
	\caption{Examples of tinnitus spectrograms from the American Tinnitus Association website \cite{Symptoms2015}.
	These spectrograms are heterogeneous as well as high-dimensional; the signals contain many frequency bands and vary over time.}
	\label{fig:tinnitusexamples}
\end{figure}

@@

Reverse correlation has been increasingly used for inferring higher-level cognitive representations as well,
including psychophysical kernels that drive the top-down processes of perception
\cite{ahumadaStimulusFeaturesSignal1971, neriReceptivePerceptiveFields2006,gosselinSuperstitiousPerceptionsReveal2003,smithMeasuringInternalRepresentations2012}, 
and even abstract psychological
categories (\eg ``male'' vs. ``female'' faces; \cite{brinkmanVisualisingMentalRepresentations2017,manginiMakingIneffableExplicit2004,ponsotCrackingSocialCode2018}.
Recent work in vision has demonstrated that
reverse correlation can effectively characterize cognitive representations underlying letter and face
recognition \cite{gosselinSuperstitiousPerceptionsReveal2003,liuSeeingJesusToast2014}.
One speech study has also estimated steady-state representations of vowels /a/
and /i/ using a closely-related paradigm to the one proposed here (Fig 2B; \cite{brimijoinInternalRepresentationVowel2013}). Our
proposed use of reverse correlation in the domain of speech expands on classic efforts to understand
top-down processing in speech with the presentation of rich, vague stimuli to elicit responses from
listeners \cite{warrenAuditoryIllusionsConfusions1970,vokeySubliminalMessagesDevil1985}.
These studies provide clear evidence that rich
stimuli, such as white noise, are sufficient to engage the top-down process, even if they do not attempt to
characterize the latent representations.

Incomplete characterizations of cognitive representations impoverish our scientific understanding of tinnitus,
weaken causal explanations for its etiology, and hinder progress towards effective treatments.
Reverse correlation shows promise to provide a more complete characterization of cognitive representations of tinnitus
and is applicable to other psychophysical domains as well.
Directly characterizing complex representations of tinnitus can enable more effective, targeted treatments,
reveal insights about subtypes of the condition, and pave the way for new tinnitus-masking assistive devices.
Fully characterizing a high-dimensional representation of tinnitus will improve causal explanations
for currently unexplained variability in tinnitus experience both between subjects and within single subjects over time.

% \begin{description}
% 	\item[A.3. Rigor of the Prior Research]{}
% \end{description}

@@

In the proposed project, we will use reverse correlation to reveal unbiased high-dimensional
representations of tinnitus and further characterize the condition
using dimensionality-reduction and density-based clustering.
We will use data regarding the space of tinnitus Representations
to iteratively improve our stimulus generation and representation classification algorithms.
In \emph{Aim \#1}, we will develop and run an experimental paradigm
in which tinnitus patients listen to noisy stimuli and perform an alternate forced-choice task
answering the question, ``Does this sound like your tinnitus?''
Instead of using limited, preconstructed stimuli, we will randomly sample from a distribution.
Reverse correlation frees us from the methodological constraint of imposing strong \emph{a priori}
assumptions about the tinnitus percept.
In \emph{Aim \#2}, we will develop an open-source signal processing pipeline
to reconstruct cognitive representations of tinnitus using compressive sensing.
Compressive sensing holds promise to dramatically reduce the number of samples
needed for accurate reconstruction, enabling us to run more experimental subjects for Aim \#1,
and retest subjects to examine the stability of cognitive representations of tinnitus over time.
\emph{Aim \#3} contextualizes reconstructed cognitive representations of tinnitus
by visualizing underlying subtypes or clusters on a lower dimensional manifold.
We will employ dimensionality reduction and clustering algorithms to represent and visualize the data,
providing direct insight into commonalities and variability of tinnitus experience in and between subjects.
Furthermore, we will use information about the distribution of representations
to iteratively improve our stimulus generation and data-driven subtype classification processes.

@@

Two common approaches are alternate forced choice tasks with constructed stimuli
and likeness measures.
In the former experimental paradigm,
the experimenter presents participants with multiple samples of auditory stimuli that vary in well-characterized
and often highly-constrained ways, along specific dimensions (\eg pure tone frequency, width of spectral envelope)
that are known to be, or are hypothesized to be, relevant to tinnitus representation or masking
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,henryMeasurementTinnitus2016}.
The subject then makes a choice between stimuli.
While new methodological advances in experiment design and technology have streamlined this approach
\cite{korthOneStepCloser2020,henryComputerautomatedTinnitusAssessment2004,henryComputerautomatedTinnitusAssessment2013},
it is still constrained by \emph{a priori} assumptions about the nature of tinnitus percepts.
In contrast, likeness approaches use subjective judgment tasks,
in which the subject rates how much (if at all) a presented stimulus is part of or masks their tinnitus percept
\cite{norenaPsychoacousticCharacterizationTinnitus2002}.
While likeness measures provide more complete reconstructions of tinnitus cognitive representations,
likeness tests are time-consuming and generally not used in clinical practice
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021}.

@@

Reverse correlation has been applied across multiple fields to reveal underlying representations by application of unconstrained, noisy input.
It has been used to characterize low-level latent representations encapsulated in neural tuning
(\eg receptive fields) \cite{ringachReverseCorrelationNeurophysiology2004}
and has been used to successfully recover cognitive representations underlying visual perception \cite{gosselinSuperstitiousPerceptionsReveal2003,}
Both existing experimental work (\cf Fig 2B in \cite{brimijoinInternalRepresentationVowel2013})
and our preliminary simulation experiments (\autoref{fig:csexample}) suggest that this method can be successfully translated
into the auditory domain.
Reverse correlation allows us (\emph{a}) to uncover more complex, potentially higher-dimensional representations
than would be possible using more focused, constrained stimuli,
(\emph{b} to recover directly the nature of the representations themselves rather than the relation
between the tinnitus percept and a masking sound,
and (\emph{c}) to recover cognitive representations of the tinnitus percept directly rather than a neural correlate.
In short, reverse correlation will be able to provide deeper understanding of cognitive representations of tinnitus percepts
than is possible with conventional methods.

@@

Our preliminary testing suggests that truly random envelopes
often result in the perception of colored noise.
Minimal additional spectral-temporal constraints may need to be imposed on stimuli
such that participants will interpret the stimuli as intending to be tinnitus percepts.
This is similar to the approach taken in some visual domain experiments,
where bandlimited random stimuli, or stimuli with partial superimposed templates,
are presented \cite{smithMeasuringInternalRepresentations2012}.
The basic approach will be to use inverse Fourier transforms to generate 0.5-s noise stimuli
including frequencies from 0.1 to 22 kHz \cite{brimijoinInternalRepresentationVowel2013}.
We will impose minimal constraints on the stimuli generation process,
in order to selectively generate stimuli approaching the heterogeneous samples of tinnitus percepts
provided by the American Tinnitus Association on their website \cite{Symptoms2015}.

@@

During the experiment, subjects will be asked to perform an computerized alternate forced-choice task,
selecting whether the presented stimulus sounds similar to their tinnitus percept or not.
They will be told that the stimuli are representations of tinnitus from other patients.
Each signal will be presented to subjects over headphones
at an audible level ($\approx 75$ dB SPL) after which
the subject will select either ``yes'' or ``no'' via keyboard presses.
The next trial will begin after a 500-ms pause.
Subjects will be asked to perform the task in hour-long blocks with a rest period in-between.
Subjects can perform the task for one or more blocks at their choice,
and will be compensated for their participation.

@@

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_3.png}
	\caption{Schematic overview of experiments proposed in Aim \#1.
	Subjects are presented with random stimuli,
	which is compared to a latent internal representation.
	Reverse correlation is used to reconstruct an estimate of the latent internal representation
	over many trials.
	Simulation results are shown, demonstrating proof-of-concept
	for the proposed reverse correlation paradigm.}
	\label{fig:experiment}
\end{figure}

@@

We have conducted simulation studies to begin validating compressive sensing
for improving the efficiency of reverse correlation.
For example, using a template time-frequency representation, $x$,
as a proxy for the latent representation of interest,
we generate plausible yes/no subject responses, $y \in \{-1, 1\})$,
based on the similarity between the template
and a random stimuli (\ie $y = \mathrm{sign}(\phi x)$ for stimuli $\phi$).
Estimation of the template is performed using
(\emph{a}) convention regression-based reverse correlation
(\ie $\hat{x}_c = n^{-1} X^\mathrm{T}y$) \cite{gosselinSuperstitiousPerceptionsReveal2003},
or (\emph{b}) compressive sensing.

@@

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=\textwidth]{Figures/CompSensExamples.pdf}
	\caption{Compressive sensing (CS) delivers accurate signal reconstruction from sampling
	with a comparatively small number of samples.
	The latent representation in (\emph{A}) is estimated in (\emph{B-E}).
	In (\emph{B-C}) conventional regression-based estimation is used
	and in (\emph{D-E}) compressive sensing is used.
	The number of samples, $n$, is displayed along with the correlation coefficient, $r^2$,
	between the estimated reconstruction and the original signal,
	as a measure of reconstruction quality.}
	\label{fig:csexample}
\end{figure}

@@

Surveys of tinnitus patients have identified sixteen qualitative subtypes of tinnitus
\cite{vajsakovicPrinciplesMethodsPsychoacoustic2021,meikleTinnitusArchiveArchive2004,stoufferCharacterizationTinnitusTinnitus1990},
but these categories are limited by the fuzziness of linguistic categories and the musical ability of the tinnitus patients.
Tinnitus subtypes are used to better explain and quantify the condition,
however qualitative subtypes are ill-defined.
While one tinnitus patient we interviewed, who has a degree in music performance,
was able to identify her tinnitus as sounding like a particular note played on the crotales,
a niche percussion instrument,
most tinnitus patients lack the depth of vocabulary to explain their tinnitus percept that precisely.
Accordingly, linguistic description of tinnitus can be vague and overlapping.
For instance, two of the subtypes in \cite{vajsakovicPrinciplesMethodsPsychoacoustic2021} are ``high tension wire'' and ``transformer noise.''
Is ``high tension wire'' meant in the colloquial sense of high-voltage power lines,
or does it mean the reverberation of a tightly-pulled string?
If the latter, then how is the sound of a high-voltage power line
disambiguated from the sound of a distribution transformer,
which is
mounted on a utility pole and connected directly to the high-voltage wires?
Instead of linguistic categories, we propose to use latent variable analysis
to reveal data-driven subtypes of tinnitus.

We will perform a quantitative analysis of tinnitus representations based on latent variable analysis methods
to reveal underlying similarities between representations.
Latent variable methods relate observed variation (\eg in tinnitus representations)
to latent variables that capture the observed variation (\eg major variation types across tinnitus percepts).
We will use principle component analysis (PCA) and uniform manifold approximation and projection (UMAP; \cite{mcinnesUMAPUniformManifold2020}).
Applying these dimensionality-reduction algorithms to a collection of representations
will identify major modes of variation across those representations,
uncovering latent similarities between representations.
Clusters of data points become readily visible in the lower-dimensional manifold generated
by these unsupervised machine learning methods, each of which represents
a data-driven tinnitus subtype (\autoref{fig:dimredexample}).
We will characterize these subtypes, identifying their properties and assigning them descriptive names.
New data can be mapped into the lower-dimensional manifold,
allowing representations from new subjects to be classified into these subtypes.

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/umap.png}
	\caption{Tinnitus representations with different spectral characteristics cluster in a lower dimensional manifold.
	Tinnitus representation waveforms were generated
	using examples from the American Tinnitus Association website with added Gaussian noise
	\cite{Symptoms2015}.
	(\emph{a}) shows the frequency spectra for representative waveforms. (\emph{b}) The waveforms
	are dimensonally-reduced using UMAP from 8,193 dimensions to 2.
	The waveforms cluster in this lower dimensional space, revealing latent similarities.}
	\label{fig:dimredexample}
\end{figure}

@@

In Aim \#1, we generate stimuli by randomly sampling Fourier coefficients from a flat distribution to generate a spectrum.
We enforce only minimal constraints on the stimuli (\eg that the frequency content is audible).
This has the benefit of reducing bias in the reconstructed representations,
but results in experiments that take longer to converge to a good reconstruction.
Previous studies using reverse correlation have attempted to reduce noise in the reconstructed representation
(and thus converge much faster) by carefully selecting stimuli biased towards a certain representation.
For example, Smith and colleagues \cite{smithMeasuringInternalRepresentations2012}
devised a task to uncover cognitive representations of faces using reverse correlation,
using pictures of human faces distorted by noise as stimuli for the task.
While this allowed the experimenters to perform fewer trials to achieve good reconstructions,
it introduced bias of what experimenters think human faces look like (by selecting the pictures),
defeating one of the main advantages of reverse correlation.
